\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Snapshot Objectives: Knowledge Expiration Tracker}
\author{Daniel Yang, Chad Wong, Raymond Diep, William Lopez, Liam Peak}
\date{\today}

\begin{document}

\maketitle

\section{Snapshot 1: Start Objective} 
The objective for Snapshot 1 was to establish the project's foundational framework and management infrastructure. We successfully initialized the GitHub repository, configured the Dockerized environment (React, Node.js, and PostgreSQL), and mapped the system architecture via a high-level workflow diagram. Additionally, we established a 1-month sprint in Jira to track task delegation and version control.

\section{Snapshot 2: 1st Checkpoint Objective}
The objective for Snapshot 2 is to implement the first "Large Feature," focusing on the core Knowledge Entry system. This includes developing the user interface for inputting expiration data and the backend logic for storage. We will also initiate formal QA processes by generating our first TestRail summary report to identify initial system weaknesses and ensure the Docker container handles the new dependencies for the frontend and backend services.

\section{Snapshot 3: 2nd Checkpoint Objective}
The objective for Snapshot 3 is to integrate the Notification and Alert system. This feature will track expiration dates and trigger automated alerts for the user. Documentation will be updated to include revised SDD and SRS sections reflecting the logic for time-based triggers. We will perform regression testing, documented via TestRail, to ensure that the new alert system does not conflict with the existing database architecture established in previous phases.

\section{Snapshot 4: Due Date Checkpoint}
The final objective is to reach full system stability and project completion. This involves a comprehensive review of all LaTeX documentation (SDD, SRS, Design Spec, and User Manual) to ensure they accurately reflect the final product. We will conduct a final end-to-end test run, generating a concluding TestRail summary report. The focus will be on UI/UX polishing, ensuring the Docker-compose deployment is seamless, and verifying that all project goals identified in the initial Jira backlog have been met.

\end{document}
