\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Software Requirement Specification: Knowledge Expiration Tracker}
\author{Daniel Yang, Chad Wong, Raymond Diep, William Lopez, Liam Peak}
\date{May 12, 2026}

\begin{document}

\maketitle
\newpage
\tableofcontents
\newpage

\section{Versions Table}
\begin{tabular}{|l|l|l|l|}
\hline
\textbf{Version} & \textbf{Date} & \textbf{Description} & \textbf{Author} \\ \hline
1.0 & 05/12/2026 & Snapshot 1: Initial Requirements & Group \\ \hline
\end{tabular}

\section{Introduction}
The Knowledge Expiration Tracker is a specialized tool designed to help students and professionals retain information by tracking the "expiration" of learned concepts based on the forgetting curve.

\section{External Interface Requirements}
The system will interface with modern web browsers (Chrome, Firefox, Safari) via a React-based UI. It requires a stable internet connection to sync data with the PostgreSQL database.

\section{Legal and Ethical Considerations}
The Knowledge Expiration Tracker handles personal user data, specifically learning habits and academic progress. To ensure ethical compliance, the system must implement strict data privacy protocols, ensuring that no third party can access a user’s study history without explicit consent. Furthermore, we must address the 'Right to be Forgotten' by allowing users to permanently delete their profiles and associated data. Legally, the project will adhere to standard data protection practices, utilizing JWT for secure session management and hashing passwords.

\section{Glossary}
Refer to the System Design Document for technical definitions.

\end{document}
